Search-Based Test Data Generation for JavaScript Functions with DOM

### 2017-12-23 doc/icse2018/icse2018.tex
Explained research RQ2.
* doc/icse2018/icse2018.tex:

\usepackage{syntax}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{pgfplots}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}
\newcommand{\thenBr}{\text{then}}
\newcommand{\elseBr}{\text{else}}
\newcommand{\inFor}{\text{inFor}}
\newcommand{\inWhile}{\text{inWhile}}

@@

\begin{table}
  \caption{Genetic Operation for JS types}
  \label{tbl.gen.oper.js.types}
    \footnotesize
  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
    \toprule
    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
    \midrule
    Random & Bool & choose at random \{\texttt{true}, \texttt{false}\} \\
    Random & Int  & with 80\% probability choose an integer from [-10, 10], or with 20\% from integer constants\\
    Random & Float & with 80\% probability choose an float from [-10.0, 10.0], or with 20\% from float constants\\
    Random & String & with 80\% probability make a random string up to length five composed characters \texttt{[a-zA-Z0-9]}, or with 20\% from string constants\\
    Random & Array & make a random array of a respective type upto length five\\
    \midrule
    Crossover & Bool   & pick at random one out of two given boolean \\
    Crossover & Int    & pick at random one out of two given integers\\
    Crossover & Float  & pick at random one out of two given floats\\
    Crossover & String & choose independently crossover point for each string, swap ends, and pick result at random\\
    Crossover & Array & similar crossover operator as for strings\\
    \midrule
    Mutation & Bool & Flip the boolean constant\\
    Mutation & Int  & Generate a new integer value, on increase (decrease) by 1 or 10 the given one\\
    Mutation & Float  & Generate a new float value, on increase (decrease) by 0.1, 1 or 10 the given one\\
    Mutation & String & Generate an new string values, remove a random character in a string, or replace a successor (predecessor) a random character\\
    Mutation & Array & Mutate a random element in array according to its type\\
    \bottomrule
  \end{tabular}
\end{table}

@@

In order to evaluate practical feasibility of the test framework adoption, we conducted an empirical validation on a set of case studies. Table~\ref{tbl.gen.config} gives summary of configuration parameters for both random and genetic instances of our framework. As a baseline we implemented random test generation strategy. It is similar to the genetic one except that it won't performing crossover and mutation. Hence, it also benefits from initial static analysis and follow up dynamic constant propagation. In addition, we experimented with two different sizes (5 and 10) for genetic restart in case of archive convergence.

\begin{table}
  \caption{Genetic Algorithm Configurations}
  \label{tbl.gen.config}
    \footnotesize
  \begin{tabular}{l|r|r}
    \toprule
    \textbf{Parameter Name} & \textbf{Random} & \textbf{Genetic} \\
    \midrule
    Population size                   & 50  & 50 \\
    Archive size                      & 1   & 25 \\
    Maximum number of generations     & 200 & 200 \\
    Crossover rate                    & 0   & 0.5 \\
    Mutation rate                     & 0   & 0.5 \\
    History window size               & 200 & 5/10/200 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Being one of the most popular programming languages of modern time, there are ample open source JS projects on the Web. Being written with the help of countless number of specialized JS libraries, JS applications greatly vary in size, complexity and coding style. Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation. In order to choose suitable case-studies, we need to scrutinize the source code of the JS applications which is time consuming and labor intensive process. Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}. Both of these works address the problem of testing of JS application with the reference to the browser DOM. Since our testing framework is capable of dealing with the browserless imperative JS code as well, we introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}}. For each case-study application, we identified several JS functions that are suitable for our testing framework. In the end, our evaluation set included both primitive and DOM related JS functions.

Table~\ref{tbl.case.studies} presents common quantitative characteristics of the selected functions such as the number of branches (\textbf{\#BR}), lines of code (\textbf{\#LOC}) and cyclomatic complexity (\textbf{CC}). The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.

Consider examples from: \cite{artemis2011}, \cite{dom2011}...

To report on cyclomatic complexity we use \emph{jshint}\footnote{http://jshint.com/} (we can also use this tool\footnote{http://jsmeter.info/})

\begin{table*}
  \caption{Summary of the case studies}
  \label{tbl.case.studies}
  %\resizebox{\textwidth}{!}{
    \scriptsize
  \begin{tabular}{l|l|l|r|r|r|r|c|c|c|c}
    \toprule
    \textbf{case-study} & \textbf{function} & \textbf{type} & \textbf{\#LOC} & \textbf{\#BR} & \textbf{\#D} & \textbf{CC} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
    \midrule
    sudoku     & helpMe & (dom,int,int)                                   & 15 & 2  & 3 & 3  & + & + & + & - \\
    sudoku     & isGameFinished & (dom)                                   & 17 & 4  & 3 & 5  & + & + & + & + \\
    sudoku     & newGame & (dom)                                          & 12 & 1  & 2 & 2  & + & + & + & + \\
    sudoku     & revealAll & (dom)                                        & 14 & 0  & 2 & 1  & + & + & + & - \\
    sudoku     & showCell* & (dom)                                         &    &    &   &    &   &   &   & \\
    sudoku     & shuffleBoard & (dom)                                     & 26 & 2  & 3 & 3  & + & - & + & - \\
    sudoku     & switchLevel* & (dom,bool)                                 &    &    &   &    &   &   &   & \\
    \midrule
    phormer    & toggleInfo & (dom,string)                                & 15 & 3  & 1 & 4  & + & + & - & - \\
    phormer    & update* & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) &    &    &   &    &   &   &   & \\
    phormer    & updateIndic* & (dom,bool)                                 &    &    &   &    &   &   &   & \\
    \midrule
    hotel RS    & RequiredField* & (dom,[string])                           &    &    &   &    &   &   &   & \\
    hotel RS   & isValidCard & ([int])                                    & 20 & 2  & 2 & 5  & - & - & - & - \\
    hotel RS   & isValidMasterCard & ([int])                              & 6  & 4  & 1 & 7  & - & - & - & - \\
    hotel RS    & isValidVISA & ([int])                                    &    &    &   &    &   &   &   & \\
    hotel RS    & validateNumber* & (dom,string)                            &    &    &   &    &   &   &   & \\
    \midrule
    apophis    & doRain* & (dom,string,int,int,int,int,int,int)            &    &    &   &    &   &   &   & \\
    apophis    & drawShields* & (dom,[int])                                &    &    &   &    &   &   &   & \\
    apophis    & fireMeteor* & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) &    &    &   &    &   &   &   & \\
    apophis    & getReady* & (dom,int,int,int,int,int,int)                 &    &    &   &    &   &   &   & \\
    apophis    & initShields & (dom,[int],int,int)                        & 8  & 0  & 1 & 1  & + & + & - & -\\
    \midrule
    bingbong   & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & + & + & - & - \\
    bingbong   & initBricks & (dom,[int],int,int)                         & 63 & 12 & 4 & 13 & + & + & - & - \\
    bingbong   & doPaddlePower & (dom,int,int)                            &    &    &   &    &   &   &   & \\
    bingbong   & drawLevel* & (dom,int,int,int,int)                        &    &    &   &    &   &   &   & \\
    bingbong   & goPing* & (dom,int,int,int)                               &    &    &   &    &   &   &   & \\
    \midrule
    burncanvas & do\_draw & (int,int,int,int,int,int,int)                 & 39 & 12 & 2 & 14 & - & - & - & - \\
    \midrule
    cs-in-js   & luhn-algorithm* & (string,bool)                           &    &    &   &    &   &   &   & \\
    cs-in-js   & quicksort-partition* & ([int],int,int)                    &    &    &   &    &   &   &   & \\ 
    \midrule
    mathjs     & prob\_gamma & (float)                                    & 56 & 8  & 2 & 16 & - & - & - & - \\
    \bottomrule
  \end{tabular}
%}
\end{table*}

\begin{description}
\item[\textbf{Q1}] What is the performance of our test generation framework?
\item[\textbf{Q2}] How does genetic version perform against the random one?
\item[\textbf{Q3}] How does the restart of genetic algorithm after the archive convergence enhance the performance? 
\end{description}

\setlength\tabcolsep{2pt}
\begin{table*}
  \caption{Statistics for genetic and random algorithms}
  \label{tbl.stats}
  \scriptsize
  %\resizebox{\textwidth}{!}{

    \begin{tabular}{l|rrrr|rrrr|rrrr|rrrr|rrrrrr}

@@

      \textbf{NAME}   & $\mathbf{\bar{x}_R}$     & $\mathbf{\bar{x}_G}$   & $\mathbf{\bar{x}_{G5}}$ & $\mathbf{\bar{x}_{G10}}$ & $\mathbf{m_R}$       & $\mathbf{m_G}$     & $\mathbf{m_{G5}}$     & $\mathbf{m_{G10}}$   & $\mathbf{mn_R}$  & $\mathbf{mn_G}$ & $\mathbf{mn_{G5}}$ & $\mathbf{mn_{G10}}$ & $\mathbf{mx_R}$  & $\mathbf{mx_G}$ & $\mathbf{mx_{G5}}$ & $\mathbf{mx_{G10}}$ & \textbf{R-G} & \textbf{R-G5} & \textbf{R-G10} & \textbf{G-G5} & \textbf{G-G10} & \textbf{G5-G10}\\
      \textbf{helpMe} & 293    & 63.18 & 78.34 & 80.68 & 270 & 47   & 59.5 &  55.5 & 33   & 7    & 8      & 12     & 609 & 258 & 368  & 468 & & & & & & \\
    $(3,4,\inFor)$    & 5.34   & 6.24  & 8.48  & 9.32  & 4   &  3    & 6    &  6    & 1     & 1    & 1      & 2       & 21   &  23   &  48    & 84  & 0.57 & 0.41 & 0.39 & 0.38 &  0.37 & 0.47 \\
    $(5,6,\thenBr)$   & 5.74   & 9.86  &  7.76  & 8.06  & 5   & 5.5  & 4    & 5    & 2     & 1    & 1      & 1       & 28   & 68   & 38    & 89  & 0.46 & 0.47 & 0.5  & 0.52 & 0.53 & 0.52 \\
    $(5,15,\elseBr)$  & 151.48 & 27.08 & 32.7  & 31.92 & 156 & 20.5 & 28.5 & 23.5 & 6     & 3    & 3      & 2       & 294 & 99   & 156  & 130 & 0.87 & 0.85 & 0.86 & 0.42 & 0.48 &  0.55 \\
    $(9,10,\thenBr)$  & 124.26 & 15.58 & 21.66 & 21.9  & 101 & 14   & 17   & 17   & 23   & 1    & 2      & 6       & 245 & 51   & 83    & 86  & 0.98 & 0.95 & 0.95 & 0.43 & 0.40 & 0.47 \\
    $(9,14,\elseBr$   & 6.18   & 4.42  & 7.74  & 9.48  & 4 & 4 & 4 & 4 & 1 & 1 & 1 & 1 & 21 & 17 & 43 & 79 & 0.56 & 0.53 & 0.51 & 0.48 & 0.45 & 0.48 \\
    \midrule
    \textbf{isGameFinished}      & 290.26 & 135.06 & 75.68 & 77.48 & 219.5 & 30   & 39   & 43   & 142 & 2   &  3    & 5       & 573 & 668 & 676  & 513 &             &              &             &             &             &      \\
    %% $(5,6,\inFor)$   & 0        & 0.88      & 0.94   & 0.94    & 1       & 1     & 1       & 1     & 0     & 0   & 0     & 0       & 2     & 3     & 3      & 3     & 0.53 & 0.5   & 0.5  & 0.48 & 0.47  & 0.5 \\
    $(7,8,\thenBr)$     & 63.68   & 40.32   & 19.62 & 15.62 & 29.5 & 7.5   & 9.5     & 12.5 & 0     & 0   & 1     & 1       & 191 & 225 & 196  & 77   & 0.6  & 0.66   & 0.66 & 0.46 & 0.43 & 0.44  \\
    %% $(7,15,\elseBr)$ & 0.98        & 0.82     & 0.84   & 0.9    & 1       & 1     & 1       & 1     & 0     & 0   & 0     & 0       & 3     & 3     & 2      & 3     & 0.57 & 0.55  & 0.54 & 0.48  & 0.46 & 0.48 \\
    $(10,11,\thenBr)$   & 166.32*    & 36.6    & 22.5  & 26.44 & 167*   & 10   & 10.5   & 11    & 141 & 2   & 1     & 3       & 191 & 220 & 217  & 224 & 0.88 & 0.96  & 0.96 & 0.52 & 0.48 & 0.45 \\
    $(10,14,\elseBr)$   & 59.28   & 56.44   & 31.78 & 33.58 & 21   & 10.5 & 17   & 17.5 & 1     & 0   & 1     & 1       & 186 & 217 & 258  & 206 & 0.55  & 0.57 & 0.55  & 0.48  &0.46 & 0.47 \\
    \midrule
    \textbf{newGame}             & 18.26 & 11.28 & 11.94  & 10.5   & 13.5   & 9   & 10    & 10   & 1      & 1    & 1      & 0       & 69  & 53    & 39    & 34 & & & & & & \\
    %% $(4,5,\inFor)$   & 0.9    & 0.66   & 0.84     & 0.86      & 1       & 1     & 1       & 1     & 0     & 0    & 0      & 0       & 2    & 2      & 2      & 1   & 0.6  & 0.53 & 0.51 & 0.42  & 0.4 & 0.49 \\
    $(6,7,\thenBr)$     & 16.58 & 9.78  & 10.24   & 8.84   & 11.5   & 7   & 8     & 8     & 1     & 1    & 1      & 0       & 67  & 47    & 34    & 31 & 0.64 & 0.6  & 0.65 & 0.44 & 0.5 & 0.56 \\
    %% $(6,12,\elseBr)$ & 0.78   & 0.84   & 0.86     & 0.8    & 1       &  1     & 1       & 1     & 0     & 0    & 0      & 0       & 2    & 4      & 3      & 2   & 0.5   & 0.47 & 0.49 & 0.46 & 0.48 & 0.52 \\
    \midrule
    \textbf{revealAll}           & 69.2   & 55.26 & 70.34 & 64.04 & 50     & 44   & 58.5 & 52.5 &  8     & 16  & 16    & 16     & 261 & 153  & 226  & 202 & & & & & &\\
    $(2,3,\inFor)$      & 27.78 & 26.7  & 39.34 & 32.58 & 20     & 24   & 30.5   & 27   & 3     & 7    & 7      & 11     & 89  & 64    & 148  & 100  & 0.45 & 0.37 & 0.39 & 0.39 & 0.43 & 0.55 \\
    $(4,5,\inFor)$      & 41.42 & 28.56 & 33.02  & 31.46 & 30     & 20   & 28   & 25.5   & 5     & 9    & 9      & 5       & 172 & 89    & 78    & 102  & 0.62 & 0.53  & 0.55 & 0.39  & 0.37 & 0.53 \\
    \midrule
    \textbf{shuffleBoard}         & 410.56 & 321.28 & 371.58 & 358.84 & 401.5 & 299   & 338 & 321 & 342 & 250 & 268 & 263 & 568 & 689 & 716 & 674 & & & & & & \\
    %% $(3,4,\inFor)$    & 1.6        & 1.36        & 1.52        & 1.42        & 2         & 1       & 2       & 1     & 1     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.61  & 0.54  & 0.58  & 0.42  & 0.47  & 0.55 \\
    %% $(5,6,\inWhile)$  & 2.94    & 2.6      &  2.58     & 2.88     &  2         & 2       &  2       &  2     & 1     & 1     & 1     & 1     & 11    & 8     & 6     & 15    & 0.6  & 0.54 & 0.56 & 0.45  & 0.46  & 0.52 \\
    %% $(10,11,\inFor)$  & 1.88       & 1.4         &  1.64        &  1.58        &  2         &  1       &  2       &  2     &  2     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.72  & 0.61  & 0.64  & 0.38  & 0.41  & 0.53 \\
    $(13,14,\thenBr)$    & 13.6    & 13.88     &  17.7     &  15.78    & 9.5       &  8.5     &  8.5     &  9.5   & 1     & 1     & 1     & 1     & 44   & 103  & 126  & 78   & 0.58 & 0.52  & 0.53  & 0.46 & 0.46 & 0.51 \\
    % $(13,16,\elseBr)$  & 1.52       & 1.4         & 1.68        & 1.5         &  1.5       &  1       &  2       & 1.5   & 1     & 1     & 1     & 1     & 3     & 2     & 2     & 2     & 0.55  & 0.42  & 0.51  & 0.36  & 0.45  & 0.59 \\
    $(17,18,\thenBr)$    & 13.76   & 23.7    &  39.58   & 34.04   &  10      &  10      &  12.5  & 1     &  1     & 2     & 2     & 2     & 73   & 248 & 180  & 248 & 0.46 & 0.38 & 0.47 & 0.4  & 0.5   & 0.55 \\
    %% $(17,20,\elseBr)$ & 2.06       & 1.84        & 1.72        & 1.8         &  2         & 2       &  2       &  2     & 1     & 1     & 1     & 1     &  4    & 2     & 2     & 2     & 0.59  & 0.64  & 0.61  & 0.56  & 0.52  & 0.46 \\
    $(21,22,\inFor)$     & 373.2*    & 275.1*     & 305.16*    & 299.84*    & 372.5*   & 273.5* & 307*   & 302* & 334 & 242 & 260 & 255 & 427 & 322 & 396 & 325 & 1     & 0.99  & 1     & 0.15 & 0.16   & 0.58 \\
    \midrule
    \midrule
    \textbf{toggleInfo}         & 6.12 & 11.9 & 18.3 & 15.4  & 5.5 & 7 & 7.5  & 6 & 0 & 0 & 0 & 0 & 22 & 118 & 138 & 106 & & & & & & \\
    $(2,3,\thenBr)$    & 2.32 & 1.64  & 1.7   & 1.46     & 1.5 & 2 & 2   & 1 & 0 0 & 0 & 0 &  0 &  11 & 4     &  4     &  3     &  0.54  &  0.53 &  0.58 & 0.48  & 0.55 & 0.57 \\
    %% $(2,5,\elseBr)$ & 0.86    & 0.84     & 0.86    & 0.8      & 1   & 1 & 1   & 1 & 0 & 0 & 0 & 0 & 2   &1     & 1     & 1     & 0.51  & 0.5   & 0.53  & 0.49  & 0.52  & 0.53 \\
    $(6,7,\thenBr)$    & 2.1  & 8.7    & 14.92  & 12.34 & 2   & 3 & 3.5 & 3 & 0 & 0 & 0 & 0 & 8   & 112 & 132 & 101 & 0.37 & 0.29 & 0.36 & 0.42 & 0.48 & 0.55 \\
    %% $(6,13,\elseBr)$& 0.84    & 0.72     & 0.82   & 0.8      & 1   & 1 & 1   & 1 & 0 & 0 & 0 & 0 & 1   & 1     & 1     & 1     &  0.56  &  0.51  & 0.52  & 0.45  & 0.46  & 0.51 \\
    \midrule
    \midrule
    \textbf{isValidCard}       & 513.66 & 7.8 & 7.96 & 8.42 & 514   & 8 &  7 & 9.5 & 447 & 5 & 5 & 5 & 579 & 12 & 13 & 12  & & & & & & \\
    %% $(3,4,\thenBr)$& 0.54     & 0.3     & 0.46    & 0.46     & 1       & 0  & 0  & 0    & 0     & 0  & 0  & 0  &  0     & 1   & 1   &  0 &  0.61 & 0.53 & 0.53 &  0.42 & 0.42 & 0.5 \\
    $(3,6,\elseBr)$   & 102.98* & 1.52 & 1.4     & 1.56  &  102.5* & 2  &  1  & 2    &  87  &  1  &  1  &  1  &  116 &  2   &  3   &  3    &  1 &  1 &  1 & 0.49    & 0.5  & 0.43 \\
    $(7,8,\inFor)$    & 102.38* & 1.44 & 1.6  & 1.58  & 103*   & 1  & 2  & 2    & 90  & 1  & 1  & 1  & 115 & 3   & 2   & 2    & 1 & 1 & 1 & 0.42 & 0.43 & 0.51 \\
    $(10,11,\thenBr)$ & 101.44* & 1.56    & 1.48 & 1.7   & 102*   & 2  & 1  & 2    & 88  & 1  & 1  & 1  & 116 & 2   & 2   & 3    &  1 &  1 &  1 &  0.54 & 0.43 &  0.4 \\
    $(10,13,\elseBr)$ & 104.66* & 1.38 & 1.54 & 1.62  & 106*   & 1  & 2  & 2    & 91  & 1  & 1  & 1  & 115 & 2   & 2   & 2    & 1 & 1 &  1 &  0.42 & 0.38 &  0.46 \\
    $(14,15,\inFor)$  & 101.66* & 1.6  & 1.48 & 1.5   & 99.5*  & 2  & 1  & 1.5  & 91  & 1  & 1  & 1  & 117 & 2   & 3   & 2    & 1 & 1 &  1 &  0.56 &  0.55 & 0.48 \\
    \midrule
    %% \textbf{isValidMasterCard}  & 109.46 & 4.84 & 5.1  & 5.03 & 102.5 & 4 & 4.5 & 4 & 86 & 2 & 2 & 2 & 164 & 11 & 11 & 10 & & & & & & \\
    %% $(2,3,\thenBr)$    & 108.98* & 4.5  & 4.64 & 4.6  & 102.5* & 4 & 4.5 & 4 & 86 & 2 & 2 & 2 & 162 & 10 & 10 & 9  & 1      & 1     & 1 & 0.47 & 0.49 & 0.51 \\
    %% %% $(2,5,\elseBr)$ & 0.48     & 0.34     & 0.46   & 0.43     & 0       &  0  &  0    & 0  & 0    & 0 & 0 & 0 & 2     & 1   & 1   & 1   & 0.56 & 0.5 & 0.52 & 0.44 & 0.46 & 0.52 \\
    \midrule

>>>>

\usepackage{syntax}
\usepackage{multirow}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{algorithmic}
\usepackage{longtable}
\usepackage{subcaption}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}
\newcommand{\thenBr}{\text{then}}
\newcommand{\elseBr}{\text{else}}
\newcommand{\inFor}{\text{inFor}}
\newcommand{\inWhile}{\text{while}}
\newcommand{\un}[1]{\underline{#1}}

@@

\begin{table}
  \caption{Genetic Operation for JS types}
  \label{tbl.gen.oper.js.types}
    \footnotesize
  \begin{tabular}{p{1cm}|p{5mm}|p{6cm}}
    \toprule
    \textbf{Operation} & \textbf{Type} & \textbf{Description} \\
    \hline
    Random & Bool & choose at random \{\texttt{true}, \texttt{false}\} \\
    Random & Int  & with 80\% probability choose an integer from [-10, 10], or with 20\% from integer constants\\
    Random & Float & with 80\% probability choose an float from [-10.0, 10.0], or with 20\% from float constants\\
    Random & String & with 80\% probability make a random string up to length five composed characters \texttt{[a-zA-Z0-9]}, or with 20\% from string constants\\
    Random & Array & make a random array of a respective type upto length five\\
    \hline
    Crossover & Bool   & pick at random one out of two given boolean \\
    Crossover & Int    & pick at random one out of two given integers\\
    Crossover & Float  & pick at random one out of two given floats\\
    Crossover & String & choose independently crossover point for each string, swap ends, and pick result at random\\
    Crossover & Array & similar crossover operator as for strings\\
    \hline
    Mutation & Bool & Flip the boolean constant\\
    Mutation & Int  & Generate a new integer value, on increase (decrease) by 1 or 10 the given one\\
    Mutation & Float  & Generate a new float value, on increase (decrease) by 0.1, 1 or 10 the given one\\
    Mutation & String & Generate an new string values, remove a random character in a string, or replace a successor (predecessor) a random character\\
    Mutation & Array & Mutate a random element in array according to its type\\
    \bottomrule
  \end{tabular}
\end{table}

@@

In order to evaluate practical feasibility of the test framework adoption, we conducted an empirical validation on a set of case studies described in Section~\ref{sub.sec.case.studies}. All the experiments were performed in a batch mode on a cluster machine with 32 HT Cores and 256 GB RAM running under Scientific Linux 7.3. We have created three different instances of our JS testing framework each is based a slight variation of the underlying genetic search algorithm. The first version is \emph{Random} ($R$), i.e. instead of applying crossover and mutation we regenerate new population from scratch. It worth to notice, that random version also benefits from both preliminary static analysis phase and dynamic constant propagation during fitness evaluation step. The second version is \emph{Genetic} ($G$) and it literally follows all of the steps prescribed by the genetic framework in Figure~\ref{fig.framework.architect}. The last version ($G10$) is based on the genetic algorithm~\ref{alg.gen} where search is restarted after the archive is converged within a given history window, which is equal to 10 in our case. Initially, we experimented with two different window sizes 5 and 10. On one hand, a smaller window size forces the GA to converge fast and early discover a potential flat space. On the other hand, it sometimes causes a premature convergence by not letting the right genetic combination to be triggered. We experimentally concluded that the window size 10 works best for our examples and present the rest of the analysis based on that result. Table~\ref{tbl.gen.config} summarizes the configuration parameters for all three proposed test generation strategies. The choice of initial values is similar to other genetic testing frameworks, e.g. \emph{EvoSuite}~\cite{evosuite}.

\begin{table}
  \caption{Genetic Algorithm Configurations}
  \label{tbl.gen.config}
    \scriptsize
  \begin{tabular}{l|r|r|r}
    \toprule
    \textbf{Parameter Name} & \textbf{R} & \textbf{G} & \textbf{G10} \\
    \hline
    Population size                   & 50  & 50  & 50  \\
    Archive size                      & 1   & 25  & 25  \\
    Maximum number of generations     & 200 & 200 & 200 \\
    Crossover rate                    & 0   & 0.5 & 0.5 \\
    Mutation rate                     & 0   & 0.5 & 0.5 \\
    History window size               & 200 & -   & 10  \\
    \bottomrule
  \end{tabular}
\end{table}

@@

Being one of the most popular programming languages of the modern time, there are ample open source JS projects on the Web. Being written with the help of countless number of specialized JS libraries, JS applications greatly vary in size, complexity and coding style. Moreover, some popular JS web-frameworks, such as jQuery and React\footnote{\url{http://todomvc.com/}}, offer an alternative approach to the native DOM manipulation. In order to choose suitable case-studies, we need to scrutinize the source code of the JS applications which is time consuming and labor intensive process. Therefore, we decided to primarily focus on the evaluation of the JS subjects well-established in the related research literature such as \emph{Confix}~\cite{amin:ase15} and \emph{TAJS}\footnote{\url{http://www.brics.dk/TAJS/dom-benchmarks/}}~\cite{dom2011}. Both of these works address the problem of testing of JS application with the reference to the browser DOM. Since our testing framework is capable of dealing with the browserless imperative JS code as well, we introduced two additional case-studies \emph{mathjs}\footnote{\url{https://github.com/josdejong/mathjs/}} and \emph{cs-in-js}\footnote{\url{https://github.com/nzakas/computer-science-in-javascript}}. For each case-study application, we identified several JS functions that are suitable for our testing framework. In the end, our evaluation set included both primitive and DOM related JS functions.

Table~\ref{tbl.case.studies} presents some common quantitative characteristics for the selected case-studies. For each function of a case-study we reported the following metrics\footnote{\url{http://jsmeter.info/} is the measurement tool}: lines of code (\textbf{\#LOC}), number of branches (\textbf{\#BR}), depth (\textbf{\#D}), cyclomatic complexity (\textbf{CC}), halstead volume (\textbf{HV}) and maintainability index (\textbf{MI}). The four rightmost columns \textbf{DOM}, \textbf{id}, \textbf{tag} and \textbf{class} indicate if the function manipulates with the \emph{dom}, \emph{id}, \emph{tag} or \emph{class} respectively.

\begin{table*}[t]
  \caption{Summary of the Case-Studies}
  \label{tbl.case.studies}
  %\resizebox{\textwidth}{!}{
    \scriptsize
  \begin{tabular}{l|c|l|l|r|r|r|r|r|r|c|c|c|c}

@@

    \textbf{case-study} & \textbf{?} & \textbf{function} & \textbf{type signature} & \textbf{\#LOC} & \textbf{\#BR} & \textbf{\#D} & \textbf{CC} & \textbf{HV} & \textbf{MI} & \textbf{DOM} & \textbf{id} & \textbf{tag} & \textbf{class} \\
    \hline
    sudoku     & + & helpMe & (dom,int,int)    & 14 & 2 & 3 & 3 & 344 & 107.58 & + & + & + & - \\
    sudoku     & + & isGameFinished & (dom)    & 10 & 3 & 3 & 4 & 370 & 112.55 & + & + & + & + \\
    sudoku     & + & newGame & (dom)           & 9  & 1 & 2 & 2 & 326 & 115.15 & + & + & + & + \\
    sudoku     & + & revealAll & (dom)         & 8  & 0 & 2 & 1 & 312 & 117.44 & + & + & + & - \\
    sudoku     & - & showCell & (dom)         & 8  & 0 & 0 & 1 & 232 & 118.46 & + & + & + & - \\
    sudoku     & + & shuffleBoard & (dom)      & 23 & 2 & 3 & 3 & 555 & 97.9   & + & - & + & - \\
    sudoku     & - & switchLevel & (dom,bool) & 10 & 1 & 2 & 2 & 257 & 114.26 & + & - & + & - \\
    \hline
    phormer    & + & toggleInfo & (dom,string)                                                      & 16 & 3 & 1 & 4 & 570  & 103.46 & + & + & - & - \\
    phormer    & - & update & (dom,int,[string],bool,[string],[string],bool,[string],[string],int) & 35 & 5 & 3 & 6 & 1190 & 87.804 & + & + & - & - \\
    phormer    & - & updateIndic & (dom,bool)                                                      & 16 & 3 & 1 & 4 & 361  & 105    & + & + & - & - \\
    \hline
    hotel RS   & - & RequiredField & (dom,[string]) & 11 & 2 & 2 & 5 & 247  & 112.16 & + & + & - & - \\
    hotel RS   & + & isValidCard & ([int])           & 17 & 2 & 2 & 5 & 351  & 103.91 & - & - & - & - \\
    hotel RS   & - & isValidMasterCard & ([int])     & 5  & 4 & 1 & 7 & 130  & 126.67 & - & - & - & - \\
    hotel RS   & + & isValidVISA & ([int])           & 6  & 3 & 1 & 6 & 104  & 124.71 & - & - & - & - \\
    hotel RS   & - & validateNumber & (dom,string)  & 7  & 1 & 1 & 4 & 98.1 & 122.87 & + & + & - & - \\
    \hline
    apophis    & - & doRain & (dom,string,int,int,int,int,int,int)                                  & 10 & 3 & 2 & 4 & 242 & 114.1  & + & + & - & -\\
    apophis    & - & drawShields & (dom,[int])                                                      & 6  & 1 & 2 & 2 & 212 & 123.19 & + & + & - & - \\
    apophis    & - & fireMeteor & (int,[int],int,[int],[int],[int],int,int,[int],[int],int,int,int) & 15 & 3 & 2 & 4 & 539 & 104.70 & - & - & - & - \\
    apophis    & - & getReady & (dom,int,int,int,int,int,int)                                       & 16 & 2 & 2 & 3 & 410 & 104.82 & + & + & - & - \\
    apophis    & + & initShields & (dom,[int],int,int)                                               & 6  & 0 & 1 & 1 & 310 & 122.12 & + & + & - & -\\
    \hline
    bingbong   & + & brickJiggler & (dom,int,int,int,[int],[int],[int],[int]) & 7  & 1  & 1 & 2  & 305  & 119.45 & + & + & - & - \\
    bingbong   & + & doPaddlePower & (dom,int,int)                            & 15 & 2  & 1 & 3  & 353  & 106.38 & + & + & - & - \\
    bingbong   & + & initBricks & (dom,[int],int,int)                         & 70 & 12 & 4 & 13 & 2380 & 72.594 & + & + & - & - \\
    bingbong   & - & drawLevel & (dom,int,int,int,int)                       & 22 & 2  & 3 & 3  & 703  & 97.816 & + & + & - & - \\
    bingbong   & - & goPing & (dom,int,int,int)                              & 12 & 2  & 2 & 3  & 268  & 110.93 & + & + & - & - \\
    \hline
    burncanvas & + & do\_draw & (int,int,int,int,int,int,int)                 & 40 & 12 & 2 & 14 & 583 & 86.214 & - & - & - & - \\
    \hline
    cs-in-js   & - & luhn-algorithm & (string,bool)                          & 20 & 3 & 2 & 6 & 308 & 101.49 & -  & -  & - & - \\
    cs-in-js   & - & quicksort-partition & ([int],int,int)                   & 21 & 1 & 1 & 3 & 309 & 101.38 & -  & -  & - & - \\ 
    \hline
    mathjs     & + & prob\_gamma & (float)                                    & 57 & 8  & 2 & 16 & 1370 & 77.121 & - & - & - & - \\
